Score-based tests of measurement invariance: Use in practice

### 2013-09-18 frontiers/frontiers.Rnw
o Revisions to frontiers ms o Added saved critical values to speed up frontiers compilation
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/semtools@262 edb9625f-4e0d-4859-8d74-9fd3b1da38cb

<<preliminaries1>>=
## packages
library("lavaan")
library("strucchange")
library("mvtnorm")
library("lattice")

@@

\readme{We need a better intro here.  The special topic is about measurement invariance, so most of this paragraph is obvious to everyone.  Maybe start with how so many other papers are about BSEM.}
Parameter invariance is a fundamental assumption for measurement model in 
developing psychometric scales. Violation of it could happen in any estimated parameter.  
In order to fix the psychometric scale, we need to specify the violating parameter.  
Moreover, in practice model misspecification is an inevitable issue to a certain extent 
and may interfere with parameter invariance specificity. A family of tests derived from 
stochastic process has been recently proposed to identify specific parameters impacted 
by measurement invariance violation. However, these tests have only been used to a limited 
type of parameter violation. It is this paper's intent to provide a detailed examination 
of the tests' performance under practical research scenarios.

@@

%% TODO Illustrate catL2BB statistic

@@

\readme{I just added LMuo to the sctest command; the range statistic is different.}
Another similar statistics is $\mathit{LM}_\mathit{uo}$ as shown in Equation~ \eqref{eq:lmuo}. We can obtain this statistic by using the following function. 
<<LM_UO>>=
## unordered LM
lm_uo <- sctest(reduced, as.numeric(yg$agegroup), parm=1:4, stat="LMuo")
round(lm_uo$p.value, 4)
@
The above command specifies that we wish to test model parameter numbers 1 through 4, which are the factor loadings supplied by lavaan.  The ordering of parameters can be obtained via the command \verb+coef(reduced)+.

@@

To carry out the tests, we can rely on the same function that we used
for the continuous test statistics.  As mentioned previously,
calculation of the ``maxLMo'' statistic (Equation~\eqref{eq:maxlmo})
can be lengthy from the need to simulate critical values.
%% This is more complicated than necessary, but it is written like
%% this so that we can load the ordinal critical values behind the
%% scenes without confusing the reader.
<<critvals,echo=FALSE,strip.white=all>>=
if(file.exists("opval1.rda")){
  load("opval1.rda")
} else {
  opval1 <- ordL2BB(gefp1)
  save(opval1, file="opval1.rda")
}
## Get test statistics using fnl=opval1 without showing it in the paper
wdmo <- sctest(reduced, as.numeric(yg$agegroup), parm=1:4, stat="WDMo")
maxlmo <- sctest(reduced, as.numeric(yg$agegroup), parm=1:4, stat="maxLMo",
                 fnl=opval1)
@ 
<<ordtest,eval=FALSE,strip.white=all>>=
wdmo <- sctest(reduced, as.numeric(yg$agegroup), parm=1:4, stat="WDMo")
maxlmo <- sctest(reduced, as.numeric(yg$agegroup), parm=1:4, stat="maxLMo")
@ 
<<pval,strip.white=all>>=
round(c(wdmo$p.value, maxlmo$p.value), 2)
@ 
In computing the ordinal test statistics, we
obtain~$p=\Sexpr{round(wdmo$p.value,2)}$
and~$p=\Sexpr{round(maxlmo$p.value,2)}$, respectively.
Both $p-$values are clearly larger than that of the 
likelihood ratio test and neither is significant at $\alpha=0.05$. 
This provides evidence that there is no measurement
invariance violation that is monotonic with age group.  Instead, given
the large sample size, the likelihood ratio test may be overly
sensitive to anomalous, non-monotonic violations at one (or a few) age groups.

In addition to test statistics, ``instability plots'' can be generated by using the \verb+fplot=TRUE+ argument within \verb+sctest.lavaan()+. Plots representing the statistics' fluctuations across levels of age group are displayed in Figure~\ref{fig:ordres}. The left panel displays the process associated with $\mathit{WDM}_o$, and the right panel displays the process associated with $\max\mathit{LM}_o$. 
%The following sentence is not correct for all statistics.  
%In both cases, the test statistics in the sequence assess a split of the observations up to age group $i$ vs. greater than $i$, and the null hypothesis is rejected if the maximum of the statistics is larger than its 5\% critical value(visualized by the horizontal red line). 
These plots display the loadings' fluctuation across age groups, with the x-axis reflecting age group and the y-axis reflecting test statistic values (larger values reflect more instability).  The red lines reflect critical values, so that the hypothesis of measurement invariance is rejected if a black line crosses the red line.  While the measurement invariance tests are non-significant, the plots imply some instability in the older age groups (15 and 16).

@@

%Or alternatively, we could use the sctest.lavaan function, but assign ordinal statistics.
\begin{figure}[H]
\caption{Fluctuation processes for the $\mathit{WDM}_o$ statistic (left panel) and the $\max\mathit{LM}_o$ statistic (right panel).}
\label{fig:ordres}
\setkeys{Gin}{width=\textwidth}
<<ordres, fig=TRUE, height=3, width=6, echo=FALSE, results=hide>>=
par(mfrow = c(1, 2), cex = 0.65)
sctest(reduced, as.numeric(yg$agegroup), parm=1:4, stat="WDMo", 
       fplot=TRUE, ylim=c(0,3.5), xlab="Age group",
       ylab = "Weighted max statistics", axes=FALSE)
axis(1, at = 1:5, labels = c("10-11", "12-13", "14", "15", "16"))
box()

@@

\section{Simulation 1}
In Simulation 1, we examined the extent to which the proposed tests
are sensitive to the specific model parameter that violates measurement
invariance.  If, say, a factor loading violates measurement
invariance, it is plausible that this violation impacts other
parameters such as factor covariances or other loadings 
associated with the factor in question.  Thus, the goal of the
simulation was to examine the extent to which the proposed tests
attribute the measurement invariance violation to the parameters that
are truly in violation.

\subsection{Methods}
To examine these specificity issues, we generated data from a
two-factor model with three indicators each (the same model used in
Merkle and Zeileis, \citeyearNP{MerZei13}). The measurement invariance
violation occurred in one of three places: the factor loadings
 $\lambda_{11}--\lambda_{62}$, the unique variance associated
 $\epsilon_{11}--\epsilon_{66}$, or the factor covariance $\sigma_{12}$.  
We then tested for measurement invariance in seven subsets of parameters: the three
individual parameters noted above, all six factor loadings $\lambda_{11}--\lambda_{62}$, 
all six unique variances $\epsilon_{11}--\epsilon_{66}$. The path diagram is shown in  
Figure~\ref{fig:path}.

\begin{figure}[H]
\caption{Path diagram representing the factor analysis model 
         used for simulations.}
\label{fig:path}
\includegraphics{PathDiagram}
\end{figure}

@@

\begin{figure}[H]
\caption{Simulated power curves for the ordered 
      $\max\mathit{LM}$ tests, the double-max test and the unordered $\max\mathit{LM}$ across three
      levels of the ordinal variable $m$, and measurement invariance 
      violations of 0--4 standard errors (scaled by $\sqrt{n}$). The violation parameter is Loading1.}
\label{fig:sim11res}
\setkeys{Gin}{width=\textwidth}
<<sim11res, fig=TRUE, height=7, width=7>>=
sim1.tmp <- sim1[sim1$parms %in% c("loading")& sim1$pars %in% c("Loading1","All Loadings","All Errors"),]
sim1.tmp$test <- factor(sim1.tmp$test)
trellis.par.set(theme = canonical.theme(color = FALSE))
mykey <- simpleKey(levels(sim1.tmp$test), points = TRUE, lines = TRUE)
print(xyplot(power ~ diff | nlevels+pars, group = ~ test, data = sim1.tmp, 
             type = "b", xlab="Violation Magnitude", ylab="Power", key=mykey))
@

@@

\begin{figure}[H]
\caption{Simulated power curves for the ordered 
      $\max\mathit{LM}$ tests, the ordered double-max test the unordered $\max\mathit{LM}$ across three
      levels of the ordinal variable $m$, and measurement invariance
      violations of 0--4 standard errors (scaled by $\sqrt{n}$). The violation parameter is Covariance}
\label{fig:sim12res}
\setkeys{Gin}{width=\textwidth}
<<sim12res, fig=TRUE, height=7, width=7>>=
sim1.tmp <- sim1[sim1$test %in% c("maxLM_o","WDM_o","LM_uo")&sim1$parms %in% c("var") &sim1$pars %in% c("All Loadings", "Covariance","All Errors") ,]
sim1.tmp$test <- factor(sim1.tmp$test)
trellis.par.set(theme = canonical.theme(color = FALSE))
mykey <- simpleKey(levels(sim1.tmp$test), points = TRUE, lines = TRUE)
print(xyplot(power ~ diff | nlevels+pars, group = ~ test, data = sim1.tmp, 
             type = "b", xlab="Violation Magnitude", ylab="Power", key=mykey))
@

@@

\begin{figure}[H]
\caption{Simulated power curves for the ordered 
      $\max\mathit{LM}$ tests, the ordered double-max test the unordered $\max\mathit{LM}$ across three
      levels of the ordinal variable $m$, and measurement invariance
      violations of 0--4 standard errors (scaled by $\sqrt{n}$). The violation parameter is Error1}
\label{fig:sim13res}
\setkeys{Gin}{width=\textwidth}
<<sim13res, fig=TRUE, height=7, width=7>>=
sim1.tmp <- sim1[sim1$test %in% c("maxLM_o","WDM_o","LM_uo")&sim1$parms %in% c("error") &sim1$pars %in% c("Error1","All Errors","All Loadings"),]
sim1.tmp$test <- factor(sim1.tmp$test)
trellis.par.set(theme = canonical.theme(color = FALSE))
mykey <- simpleKey(levels(sim1.tmp$test), points = TRUE, lines = TRUE)
print(xyplot(power ~ diff | nlevels+pars, group = ~ test, data = sim1.tmp, 
             type = "b", xlab="Violation Magnitude", ylab="Power", key=mykey))
@

@@

<<sim2>>=
## seed for replication
RNGkind(kind = "default", normal.kind = "default")
set.seed(1163)

@@

\begin{figure}[H]
\caption{Simulated power curves for the ordered 
      $\max\mathit{LM}$ tests, the double-max test and the unordered $\max\mathit{LM}$ across three
      levels of the ordinal variable $m$, and measurement invariance 
      violations of 0--4 standard errors (scaled by $\sqrt{n}$). The violation parameter is the lacking loading.}
\label{fig:sim21res}
\setkeys{Gin}{width=\textwidth}
<<sim21res, fig=TRUE, height=7, width=7>>=
sim2.tmp <- sim2[sim2$test %in% c("maxLM_o","WDM_o","LM_uo")&sim2$parms %in% c("extra")&sim2$pars %in% c("Loading1","Error1","Covariance"),]
sim2.tmp$test <- factor(sim2.tmp$test)
trellis.par.set(theme = canonical.theme(color = FALSE))
mykey <- simpleKey(levels(sim2.tmp$test), points = TRUE, lines = TRUE)
print(xyplot(power ~ diff | nlevels+pars, group = ~ test, data = sim2.tmp, 
             type = "b", xlab="Violation Magnitude", ylab="Power", key=mykey))
@

@@

\section{Appendix}
\begin{figure}[H]
\caption{Simulated power curves for the ordered 
      $\max\mathit{LM}$ tests, the double-max test and the unordered $\max\mathit{LM}$ across three
      levels of the ordinal variable $m$, and measurement invariance 
      violations of 0--4 standard errors (scaled by $\sqrt{n}$). The violation parameter is the lacking loading.}
\label{fig:sim22res}
\setkeys{Gin}{width=\textwidth}
<<sim22res, fig=TRUE, height=7, width=7>>=
sim2.tmp <- sim2[sim2$test %in% c("maxLM_o","WDM_o","LM_uo")&sim2$parms %in% c("extra+loading"),]
sim2.tmp$test <- factor(sim2.tmp$test)
trellis.par.set(theme = canonical.theme(color = FALSE))
mykey <- simpleKey(levels(sim2.tmp$test), points = TRUE, lines = TRUE)
print(xyplot(power ~ diff | nlevels+pars, group = ~ test, data = sim2.tmp, 
             type = "b", xlab="Violation Magnitude", ylab="Power", key=mykey))
@

\begin{figure}[H]
\caption{Simulated power curves for the ordered 
      $\max\mathit{LM}$ tests, the double-max test and the unordered $\max\mathit{LM}$ across three
      levels of the ordinal variable $m$, and measurement invariance 
      violations of 0--4 standard errors (scaled by $\sqrt{n}$). The violation parameter is the lacking loading.}
\label{fig:sim23res}
\setkeys{Gin}{width=\textwidth}
<<sim23res, fig=TRUE, height=7, width=7>>=
sim2.tmp <- sim2[sim2$test %in% c("maxLM_o","WDM_o","LM_uo")&sim2$parms %in% c("extra+var"),]
sim2.tmp$test <- factor(sim2.tmp$test)
trellis.par.set(theme = canonical.theme(color = FALSE))
mykey <- simpleKey(levels(sim2.tmp$test), points = TRUE, lines = TRUE)
print(xyplot(power ~ diff | nlevels+pars, group = ~ test, data = sim2.tmp, 
             type = "b", xlab="Violation Magnitude", ylab="Power", key=mykey))
@

\begin{figure}[H]
\caption{Simulated power curves for the ordered 
      $\max\mathit{LM}$ tests, the double-max test and the unordered $\max\mathit{LM}$ across three
      levels of the ordinal variable $m$, and measurement invariance 
      violations of 0--4 standard errors (scaled by $\sqrt{n}$). The violation parameter is the lacking loading.}
\label{fig:sim24res}
\setkeys{Gin}{width=\textwidth}
<<sim24res, fig=TRUE, height=7, width=7>>=
sim2.tmp <- sim2[sim2$test %in% c("maxLM_o","WDM_o","LM_uo")&sim2$parms %in% c("extra+error"),]
sim2.tmp$test <- factor(sim2.tmp$test)
trellis.par.set(theme = canonical.theme(color = FALSE))
mykey <- simpleKey(levels(sim2.tmp$test), points = TRUE, lines = TRUE)
print(xyplot(power ~ diff | nlevels+pars, group = ~ test, data = sim2.tmp, 
             type = "b", xlab="Violation Magnitude", ylab="Power", key=mykey))
@

@@

>>>>

<<preliminaries1,echo=FALSE>>=
## packages
library("lavaan")
library("strucchange")
library("mvtnorm")
library("lattice")

@@

\readme{We need a better intro here.  The special topic is about measurement invariance, so most of this paragraph is obvious to everyone.  Maybe start with a remark about approximate invariance and try to tie our topic to that somehow.}
Parameter invariance is a fundamental assumption for measurement model in 
developing psychometric scales. Violation of it could happen in any estimated parameter.  
In order to fix the psychometric scale, we need to specify the violating parameter.  
Moreover, in practice model misspecification is an inevitable issue to a certain extent 
and may interfere with parameter invariance specificity. A family of tests derived from 
stochastic process has been recently proposed to identify specific parameters impacted 
by measurement invariance violation. However, these tests have only been used to a limited 
type of parameter violation. It is this paper's intent to provide a detailed examination 
of the tests' performance under practical research scenarios.

@@

@@

\readme{I just added LMuo to the sctest command and corrected the command below; the range statistic is different.}
Another similar statistics is $\mathit{LM}_\mathit{uo}$ as shown in Equation~ \eqref{eq:lmuo}. We can obtain this statistic by using the following function. 
<<LM_UO>>=
## unordered LM
lm_uo <- sctest(reduced, as.numeric(yg$agegroup), parm=1:4, stat="LMuo")
round(lm_uo$p.value, 4)
@
The above command specifies that we wish to test model parameter numbers 1 through 4, which are the factor loadings supplied by lavaan.  The ordering of parameters can be obtained via the command \verb+coef(reduced)+.

@@

To carry out the tests, we can rely on the same function that we used
for the continuous test statistics.  As mentioned previously,
calculation of the ``maxLMo'' statistic (Equation~\eqref{eq:maxlmo})
can be lengthy from the need to simulate critical values.
%% This is more complicated than necessary, but it is written like
%% this so that we can load the ordinal critical values behind the
%% scenes without confusing the reader.
<<critvals,echo=FALSE,strip.white=all>>=
if(file.exists("opval1.rda")){
  load("opval1.rda")
} else {
  gefp1 <- gefp(reduced, fit=NULL, order.by=as.numeric(yg$agegroup),
                vcov=info_full, sandwich=FALSE, parm=1:4)
  opval1 <- ordL2BB(gefp1)
  save(opval1, file="opval1.rda")
}
## Get test statistics using fnl=opval1 without showing it in the paper
wdmo <- sctest(reduced, as.numeric(yg$agegroup), parm=1:4, stat="WDMo")
maxlmo <- sctest(reduced, as.numeric(yg$agegroup), parm=1:4, stat="maxLMo",
                 fnl=opval1)
@ 
<<ordtest,eval=FALSE,strip.white=all>>=
wdmo <- sctest(reduced, as.numeric(yg$agegroup), parm=1:4, stat="WDMo")
maxlmo <- sctest(reduced, as.numeric(yg$agegroup), parm=1:4, stat="maxLMo")
@ 
<<pval,strip.white=all>>=
round(c(wdmo$p.value, maxlmo$p.value), 2)
@ 
In computing the ordinal test statistics, we
obtain~$p=\Sexpr{round(wdmo$p.value,2)}$
and~$p=\Sexpr{round(maxlmo$p.value,2)}$, respectively.
Both $p$-values are clearly larger than that of the 
likelihood ratio test and neither is significant at $\alpha=0.05$. 
This provides evidence that there is no measurement
invariance violation that is monotonic with age group.  Instead, given
the large sample size, the likelihood ratio test may be overly
sensitive to anomalous, non-monotonic violations at one (or a few) age groups.

In addition to test statistics, ``instability plots'' can be generated by using the \verb+fplot=TRUE+ argument within \verb+sctest.lavaan()+. Plots representing the statistics' fluctuations across levels of age group are displayed in Figure~\ref{fig:ordres}. The left panel displays the process associated with $\mathit{WDM}_o$, and the right panel displays the process associated with $\max\mathit{LM}_o$. 
%The following sentence is not correct for all statistics:  
%In both cases, the test statistics in the sequence assess a split of the observations up to age group $i$ vs. greater than $i$, and the null hypothesis is rejected if the maximum of the statistics is larger than its 5\% critical value(visualized by the horizontal red line). 
These plots display the loadings' fluctuation across age groups, with the x-axis reflecting age group and the y-axis reflecting test statistic values (larger values reflect more instability).  The red lines reflect critical values, so that the hypothesis of measurement invariance is rejected if a black line crosses the red line.  While the measurement invariance tests are non-significant, the plots imply some instability in the older age groups (15 and 16).

@@

%Or alternatively, we could use the sctest.lavaan function, but assign ordinal statistics.
\begin{figure}
\caption{Fluctuation processes for the $\mathit{WDM}_o$ statistic (left panel) and the $\max\mathit{LM}_o$ statistic (right panel).}
\label{fig:ordres}
\setkeys{Gin}{width=\textwidth}
<<ordres, fig=TRUE, height=3, width=6, echo=FALSE, results=hide>>=
par(mfrow = c(1, 2), cex = 0.65)
sctest(reduced, as.numeric(yg$agegroup), parm=1:4, stat="WDMo", 
       fplot=TRUE, ylim=c(0,3.5), xlab="Age group",
       ylab = "Weighted max statistics", axes=FALSE)
axis(1, at = 1:5, labels = c("10-11", "12-13", "14", "15", "16"))
box()

@@

\section{Simulation 1}

In Simulation 1, we examined the extent to which the proposed tests
are sensitive to the specific model parameter that violates measurement
invariance.  If, say, a factor loading violates measurement
invariance, it is plausible that this violation impacts other
parameters such as factor covariances or other loadings 
associated with the factor in question.  Thus, the goal of the
simulation was to examine the extent to which the proposed tests
attribute the measurement invariance violation to the parameters that
are truly in violation.

\subsection{Methods}

To examine these specificity issues, we generated data from a
two-factor model with three indicators each (the same model used in
Merkle and Zeileis, \citeyearNP{MerZei13}). The measurement invariance
violation occurred in one of three places: the factor loadings
 $\lambda_{11}--\lambda_{62}$, the unique variance associated
 $\epsilon_{11}--\epsilon_{66}$, or the factor covariance $\sigma_{12}$.  
We then tested for measurement invariance in seven subsets of parameters: the three
individual parameters noted above, all six factor loadings $\lambda_{11}--\lambda_{62}$, 
all six unique variances $\epsilon_{11}--\epsilon_{66}$. The path diagram is shown in  
Figure~\ref{fig:path}.

\begin{figure}
\caption{Path diagram representing the factor analysis model 
         used for simulations.}
\label{fig:path}
\includegraphics{PathDiagram}
\end{figure}

@@

\begin{figure}
\caption{Simulated power curves for the ordered 
      $\max\mathit{LM}$ tests, the double-max test and the unordered $\max\mathit{LM}$ across three
      levels of the ordinal variable $m$, and measurement invariance 
      violations of 0--4 standard errors (scaled by $\sqrt{n}$). The violation parameter is Loading1.}
\label{fig:sim11res}
\setkeys{Gin}{width=\textwidth}
<<sim11res, fig=TRUE, height=7, width=7, echo=FALSE>>=
sim1.tmp <- sim1[sim1$parms %in% c("loading")& sim1$pars %in% c("Loading1","All Loadings","All Errors"),]
sim1.tmp$test <- factor(sim1.tmp$test)
trellis.par.set(theme = canonical.theme(color = FALSE))
mykey <- simpleKey(levels(sim1.tmp$test), points = TRUE, lines = TRUE)
print(xyplot(power ~ diff | nlevels+pars, group = ~ test, data = sim1.tmp, 
             type = "b", xlab="Violation Magnitude", ylab="Power", key=mykey))
@

@@

\begin{figure}
\caption{Simulated power curves for the ordered 
      $\max\mathit{LM}$ tests, the ordered double-max test the unordered $\max\mathit{LM}$ across three
      levels of the ordinal variable $m$, and measurement invariance
      violations of 0--4 standard errors (scaled by $\sqrt{n}$). The violation parameter is Covariance}
\label{fig:sim12res}
\setkeys{Gin}{width=\textwidth}
<<sim12res, fig=TRUE, height=7, width=7, echo=FALSE>>=
sim1.tmp <- sim1[sim1$test %in% c("maxLM_o","WDM_o","LM_uo")&sim1$parms %in% c("var") &sim1$pars %in% c("All Loadings", "Covariance","All Errors") ,]
sim1.tmp$test <- factor(sim1.tmp$test)
trellis.par.set(theme = canonical.theme(color = FALSE))
mykey <- simpleKey(levels(sim1.tmp$test), points = TRUE, lines = TRUE)
print(xyplot(power ~ diff | nlevels+pars, group = ~ test, data = sim1.tmp, 
             type = "b", xlab="Violation Magnitude", ylab="Power", key=mykey))
@

@@

\begin{figure}
\caption{Simulated power curves for the ordered 
      $\max\mathit{LM}$ tests, the ordered double-max test the unordered $\max\mathit{LM}$ across three
      levels of the ordinal variable $m$, and measurement invariance
      violations of 0--4 standard errors (scaled by $\sqrt{n}$). The violation parameter is Error1}
\label{fig:sim13res}
\setkeys{Gin}{width=\textwidth}
<<sim13res, fig=TRUE, height=7, width=7, echo=FALSE>>=
sim1.tmp <- sim1[sim1$test %in% c("maxLM_o","WDM_o","LM_uo")&sim1$parms %in% c("error") &sim1$pars %in% c("Error1","All Errors","All Loadings"),]
sim1.tmp$test <- factor(sim1.tmp$test)
trellis.par.set(theme = canonical.theme(color = FALSE))
mykey <- simpleKey(levels(sim1.tmp$test), points = TRUE, lines = TRUE)
print(xyplot(power ~ diff | nlevels+pars, group = ~ test, data = sim1.tmp, 
             type = "b", xlab="Violation Magnitude", ylab="Power", key=mykey))
@

@@

<<sim2,echo=FALSE>>=
## seed for replication
RNGkind(kind = "default", normal.kind = "default")
set.seed(1163)

@@

\begin{figure}
\caption{Simulated power curves for the ordered 
      $\max\mathit{LM}$ tests, the double-max test and the unordered $\max\mathit{LM}$ across three
      levels of the ordinal variable $m$, and measurement invariance 
      violations of 0--4 standard errors (scaled by $\sqrt{n}$). The violation parameter is the lacking loading.}
\label{fig:sim21res}
\setkeys{Gin}{width=\textwidth}
<<sim21res, fig=TRUE, height=7, width=7, echo=FALSE>>=
sim2.tmp <- sim2[sim2$test %in% c("maxLM_o","WDM_o","LM_uo")&sim2$parms %in% c("extra")&sim2$pars %in% c("Loading1","Error1","Covariance"),]
sim2.tmp$test <- factor(sim2.tmp$test)
trellis.par.set(theme = canonical.theme(color = FALSE))
mykey <- simpleKey(levels(sim2.tmp$test), points = TRUE, lines = TRUE)
print(xyplot(power ~ diff | nlevels+pars, group = ~ test, data = sim2.tmp, 
             type = "b", xlab="Violation Magnitude", ylab="Power", key=mykey))
@

@@

@@

\section{Appendix}

\readme{Need some text describing what this appendix contains.}

\begin{figure}
\caption{Simulated power curves for the ordered 
      $\max\mathit{LM}$ tests, the double-max test and the unordered $\max\mathit{LM}$ across three
      levels of the ordinal variable $m$, and measurement invariance 
      violations of 0--4 standard errors (scaled by $\sqrt{n}$). The violation parameter is the lacking loading.}
\label{fig:sim22res}
\setkeys{Gin}{width=\textwidth}
<<sim22res, fig=TRUE, height=7, width=7, echo=FALSE>>=
sim2.tmp <- sim2[sim2$test %in% c("maxLM_o","WDM_o","LM_uo")&sim2$parms %in% c("extra+loading"),]
sim2.tmp$test <- factor(sim2.tmp$test)
trellis.par.set(theme = canonical.theme(color = FALSE))
mykey <- simpleKey(levels(sim2.tmp$test), points = TRUE, lines = TRUE)
print(xyplot(power ~ diff | nlevels+pars, group = ~ test, data = sim2.tmp, 
             type = "b", xlab="Violation Magnitude", ylab="Power", key=mykey))
@

\begin{figure}
\caption{Simulated power curves for the ordered 
      $\max\mathit{LM}$ tests, the double-max test and the unordered $\max\mathit{LM}$ across three
      levels of the ordinal variable $m$, and measurement invariance 
      violations of 0--4 standard errors (scaled by $\sqrt{n}$). The violation parameter is the lacking loading.}
\label{fig:sim23res}
\setkeys{Gin}{width=\textwidth}
<<sim23res, fig=TRUE, height=7, width=7, echo=FALSE>>=
sim2.tmp <- sim2[sim2$test %in% c("maxLM_o","WDM_o","LM_uo")&sim2$parms %in% c("extra+var"),]
sim2.tmp$test <- factor(sim2.tmp$test)
trellis.par.set(theme = canonical.theme(color = FALSE))
mykey <- simpleKey(levels(sim2.tmp$test), points = TRUE, lines = TRUE)
print(xyplot(power ~ diff | nlevels+pars, group = ~ test, data = sim2.tmp, 
             type = "b", xlab="Violation Magnitude", ylab="Power", key=mykey))
@

\begin{figure}
\caption{Simulated power curves for the ordered 
      $\max\mathit{LM}$ tests, the double-max test and the unordered $\max\mathit{LM}$ across three
      levels of the ordinal variable $m$, and measurement invariance 
      violations of 0--4 standard errors (scaled by $\sqrt{n}$). The violation parameter is the lacking loading.}
\label{fig:sim24res}
\setkeys{Gin}{width=\textwidth}
<<sim24res, fig=TRUE, height=7, width=7, echo=FALSE>>=
sim2.tmp <- sim2[sim2$test %in% c("maxLM_o","WDM_o","LM_uo")&sim2$parms %in% c("extra+error"),]
sim2.tmp$test <- factor(sim2.tmp$test)
trellis.par.set(theme = canonical.theme(color = FALSE))
mykey <- simpleKey(levels(sim2.tmp$test), points = TRUE, lines = TRUE)
print(xyplot(power ~ diff | nlevels+pars, group = ~ test, data = sim2.tmp, 
             type = "b", xlab="Violation Magnitude", ylab="Power", key=mykey))
@
